Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-15 draft.tex
clean up

>>>>

\section{Alternative attempt at getting a Poincare constant estimate for the scalar potential}

\color{green}
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \\&
        \leq 
        \sum_{m=0}^{M}
        L^{\frac p q}
        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        L^{\frac p q}
        \sum_{m=0}^{M} 
        \max_{ 0 \leq \ell \leq M }
        C_{m,\ell}^{p} 
        \cdot 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}

    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
    Hence, 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \\&
        \leq 
        \sum_{m=0}^{M}
        \sum_{\ell=0}^{M} 
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \\&
        \leq 
        \max_{0 \leq \ell \leq M} \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \delta_{m,\ell} 
        \right)
        \cdot 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        \\&
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)
        \cdot 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        .
    \end{align}
    Now, if $q \leq p$, that is, $2 \leq p$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \left(
            \sum_{\ell'=0}^{M}
            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
        \right)^{\frac 1 q}
        .
    \end{align}
    Instead, if $p \leq q$, that is, $p \leq 2$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
        .
    \end{align}
    So in any case, it is better than using the following Minkowski's inequality: 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
        \\&
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
        \| \nabla u \|_{L^{p}(\Omega)}
        .
    \end{align}

\subsection{Failed uppr bound for potential operators}
On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
These do not depend on the eccentricity of the domain.

We begin with the Poincar\'e operator. 
By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{0}^{1} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{red}
A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{1}^{\infty} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{blue}
We estimate 
\begin{align*}
    \int_{0}^{1}
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    &
    \leq 
    \int_{0}^{1}
    \min\left( 
        \vol\left(\Omega\right), 
        \vol\left( \tfrac{t}{1-t} \Omega \right) 
    \right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{p(k-1)} 
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{k-1} 
    \ dt
    .
\end{align*}
The last integral is handled via the basic observations
\begin{align*}
    \int_{0}^{\frac 1 2} 
    \frac{ t^{k-1} }{ (1-t)^{n} }
    \ dt
    \leq 
    \int_{0}^{\frac 1 2} 
    (1-t)^{-n+k-1}
    \ dt
    =
    \int_{\frac 1 2}^{1} 
    t^{-n+k-1}
    \ dt
    =
    \begin{cases}
        \ln(2)                 & \text{$n=k$}
        \\
        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
    \end{cases}
\end{align*}

\subsection{Attempted proof for deformation-based estimate}

\begin{proof}\color{blue}
    We first fix some notation. 
    Recall that for any $1 \leq m \leq M$, 
    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.

    We introduce the deformation mapping $\Xi_{2,m} : \patch_{\calT}(S_m) \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{m-1} \setminus \partial T$.
    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{m} \rightarrow X_{m-1}$ 
    by letting it be the identity over $X_{m-1} \setminus A_{m-1}$.

    For each $T \in \calT$ of dimension $n$, there exists a sequence $1 \leq m_{T,1},\dots,m_{T,K} \leq M$, for some $1 \leq K \leq M$,
    such over the simplex $T$ we have the identity 
    \begin{align*}
        ...
    \end{align*}
\end{proof}

\section{Attempted global upper bound: exterior derivative case}

Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \\&
        \leq 
        \sum_{m=0}^{M}
        L^{\frac p q}
        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        L^{\frac p q}
        \sum_{m=0}^{M} 
        \max_{ 0 \leq \ell \leq M }
        C_{m,\ell}^{p} 
        \cdot 
        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    Hence, 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \\&
        \leq 
        \sum_{m=0}^{M}
        \sum_{\ell=0}^{M} 
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
        \\&
        \leq 
        \max_{0 \leq \ell \leq M} \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \delta_{m,\ell} 
        \right)
        \cdot 
        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
        \\&
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)
        \cdot 
        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
        .
    \end{align}
    Now, if $q \leq p$, that is, $2 \leq p$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \left(
            \sum_{\ell'=0}^{M}
            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
        \right)^{\frac 1 q}
        .
    \end{align}
    Instead, if $p \leq q$, that is, $p \leq 2$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
        .
    \end{align}
    So in any case, it is better than using the following Minkowski's inequality: 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
        \\&
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align}

\section{}
